### 2022-01-30 ms/PrestigeBias.tex
presentation + minor changes

\paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
\paragraph{Proof by induction:} From eq. \ref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\\\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

@@

Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
\begin{equation}
P_{fix} = \frac{1-e^{-2 S_n N_e x}}{1-e^{-2 S_n N_e}}
\end{equation}
where $S_n = ((k-l)/(k+l))*(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.

@@

We then also tried changing the composition of the cycle, by keeping a constant $n$, but changing $k,l$ accordingly.

@@

In fig.\ref{fig:ch_env_k_l} we see again that the simulations results are mostly above our modified estimation, but still contained in the area between it and the original (constant environment) estimation.
We see that the larger $k$ in relation to $l$, the closer the simulation results to the original estimation.
This was again to be expected - the larger $k$ than $l$, the more time the ideal trait has to be acquired in the population, resulting in a state where the influence alone will accelerate its fixation. So when the cycle reaches the $l$ part, the frequency of the trait is high enough to not be affected by the negative change in the environment, due to the influence.

>>>>

\paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.

The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
\paragraph{Proof by induction:}
From eq. \ref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\\\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\\\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

@@

Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
\begin{equation}
P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
\end{equation}
where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.

@@

We then also tried changing the composition of the cycle, by keeping a constant $n=40$, but changing $k,l$ accordingly.

@@

In fig.\ref{fig:ch_env_k_l} we see that the larger $k$ relative to $l$, the closer the modified equation is to the original estimation of the constant environment. 
When using higher values of $n$, the simulation results doesn't fit the equation result as with lower values. This is due to the fact that our proof, and therefore our equation is more accurate when more cycles occur. When $n$ is high, there will be less cycles, and the simulations will get closer to the constant environment equation.
